Google 表單即時回饋

### 2018-04-22 minimal_web_DataCampLight/rmarkdown/gsheet_demo.Rmd
up

```{r}
# iframe for Google Form
iframe <- HTML('<iframe src="https://docs.google.com/forms/d/e/1FAIpQLSeE-ke7yhlU3XRDIhw7vRL-mnYLi-jTOYF8Pz4ZLINjV53z2A/viewform?embedded=true" style="position: relative; height: 300px; width: 100%;" frameborder="0" marginheight="0" marginwidth="0">載入中…</iframe>')

>>>>

```{r}
# iframe for Google Form
iframe <- HTML('<iframe src="https://docs.google.com/forms/d/e/1FAIpQLSeE-ke7yhlU3XRDIhw7vRL-mnYLi-jTOYF8Pz4ZLINjV53z2A/viewform?embedded=true" style="position: relative; height: 360px; width: 100%;" frameborder="0" marginheight="0" marginwidth="0">載入中…</iframe>')
